Influence of journal data archiving mandates on author attitudes, experiences,

### 2018-03-21 manuscript.Rmd
updates to discussion

---
title: Impact of journal data archiving mandates on author attitudes, experiences,
  and practices
author: "Heather A. Piwowar, Todd J. Vision"
csl: peerj.csl
output:
  md_document:
    variant: markdown_github
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
bibliography: input_references.bib
---

@@

Journal policies as of December 2014:

@@

What has happened since

some more: `r citep(c(
bib["anagnostou2015when-da"],
bib["nosek2015scienti"],
bib["stodden2018an-empi"],
bib["budin-ljosne2014data-sh"],
bib["hate2015sweat-s"],
bib["naudet2018data-sh"],
bib["curty2017attitud"],
bib["linek2017data-sh"],
bib["longo2016data-sh"],
bib["berger2016iscbs-i"],
bib["chigusa2017state-o"],
bib["womack2015researc"],
bib["doi:10.1002/asi.23917"],
bib["plos-medicine-editors2016can-dat"],
bib["van-tuyl2016water-w"],
bib["vasilevsky2017reprodu"],
bib["doi:10.1002/asi.23336"],
bib["pearce2011data-sh"],
bib["alsheikh-ali2011public-"],
bib["vines2013mandate"],
bib["roche2014trouble"],
bib["roche2015public-"],
bib["lin2014recomme"],
bib["whitlock2016a-balan"],
bib["naughton-l2016making-"],
bib["teunis2015do-corr"],
bib["fetterman2015the-rep"]
))
`

Response to plos
Future work
With this dataset
Advanced stats
Longer term study
More jdap journals come out

## Future work

Did JDAP-adopting journals start being more eagerly adopted by people who like data archiving, or did the authors in JDAP journals change their minds?

## Limitations

@@

- IRB
- Survey questions
- Instructions to authors
- Contact corresponding code
- R files
- Raw data

@@

# Appendix: JDAP Adoption Dates

```{r, fig.width=7, fig.height=5, echo=FALSE}
library(knitr)

>>>>

---
title: Influence of journal data archiving mandates on author attitudes, experiences,
  and practices
author: "Heather A. Piwowar, Todd J. Vision"
csl: peerj.csl
output:
  md_document:
    variant: markdown_github
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
bibliography: input_references.bib
---

@@

Journal policies as of December 2014 (surveys were sent out between February 2011 and March 2014 to authors who published between November 2010 and November 2013):

@@

data policies are becoming more prevalent: seven journals announced data archiving mandates during the course of the survey (and another three journals implemented policies shortly after the suvey completed).

even so, a minority of journal policies require data sharing `r citep(c(bib["vasilevsky2017reprodu"],bib["naughton-l2016making"]))`

Even when there are journal policies, often not sufficient to achieve reproducability for the majority of studies `r citep(c(bib["roche2015public"], bib["stodden2018an-empi"], bib["naudet2018data-sh"]))`

suggesting author personality `r citep(c(bib["linek2017data-sh"]))` or social norms `r citep(c(bib["anagnostou2015when-da"], bib["womack2015researc"]))` may play a larger factor than journal policy.

Findings here are consistent with other findings that authors more likely to share data if they had prior experience sharing or reusing data
`r citep(c(bib["Piwowar_2011"]))`.

Could be helpful for journals to help spread the word about worries that are unfounded.  For example, authors are worried about scooping, but it rarely happens -- almost all of an author's papers about one of their own datasets occur within two years of its collection, whereas third-party papers are still accumulating six years later `r citep(c(bib["piwowar2013data-re"]))`.  In areas where this is less true, journal policies could be modified to support it `r citep(c(bib["whitlock2016a-balan"], bib["doi:10.1002/asi.23336"]))`

Similarily, although of course data archiving has a cost, it also has a good return on investment in terms of research output `r citep(c(bib["piwowar2011data-ar"]))`.

The longitudinal study nature of this study is useful -- comparing across journals is frought, as stronger data archiving policies are disproportionately found in higher impact journals `r citep(c(bib["vasilevsky2017reprodu"], bib["piwowar2008a-revie"]))`.

cite this? `r citep(c(bib["van-tuyl2016water-w"]))`. 
also maybe this?  `r citep(c(bib["fetterman2015the-rep"]))`.

still pulling these in to discussion notes `r citep(c(bib["budin-ljosne2014data-sh"],bib["lin2014recomme"],bib["roche2014trouble"],bib["vines2013mandate"],bib["pearce2011data-sh"],bib["alsheikh-ali2011public"]))`

Limitations of this study include:

@@

- IRB (now in dropbox)
- Recruitment emails (now in dropbox)
- Journal policies (instructions to authors as of January 29, 2011): zip of html (now in dropbox)
- Survey questions (now in dropbox)
- [Survey responses](https://github.com/hpiwowar/jdap/blob/master/data/raw_data/JDAP_Survey_Data.csv)
- [Full text comments](https://github.com/hpiwowar/jdap/blob/master/data/full_text_comments.txt)
- [Contact corresponding authors scripts](https://github.com/hpiwowar/contact_corresponding)
- [Manuscript R files](https://github.com/hpiwowar/jdap)

@@

```{r, fig.width=7, fig.height=5, echo=FALSE}
# JDAP Adoption Dates

library(knitr)
